---
title: "manhattan plot code"
author: "Michael Anderson, Eric Feczko"
format: html
editor: visual
---

### 8) Use PLSR to create weights for manhattan plot.

PLSR is used to calculate the loading weights from the model fit for the manhattan plot below. This gives an indication as to which intra and inter system connectivity may be driving effects observed in the model.

```{r}

X <- as.matrix(X0)              # n x p
y <- as.numeric(p0$y)           # length n

fit <- plsr(y ~ X, ncomp = 20,  # choose a max; tune later
  scale = FALSE, center = TRUE,
  validation = "CV",
  method = "kernelpls")
v1 <- fit$loading.weights[, 1]
```

### 9) Use ROI data to label outputs for manhattan plot.

Edit the load path to select different ROI data. Edit "V = v1" to change which PC to visual (e.g. v2, v3, etc.).

```{r}
load("ROI.RData")
# Define the inputs ManPlot expects
group_structure <- ROI$group
optional_index  <- ROI$index

# Optional: predictor names (use ROI$roi if it matches your predictors)
# Otherwise keep colnames(X)
predictor_names <- if (!is.null(ROI$roi)) ROI$roi else colnames(X)

# Sanity checks (these must match p = number of predictors)
stopifnot(length(group_structure) == length(predictor_names))
stopifnot(length(optional_index)  == length(predictor_names))
stopifnot(length(v1)              == length(predictor_names))

# Plot the first PLS "eigenvector" (loading weight vector)
ManPlot(
  V = v1,
  predictor.names = predictor_names,
  group.structure = group_structure,
  optional.index = optional_index,
  man.thresh = 0,
  point.size = 1.5
)
```