---
title: "predictions"
author: "Michael Anderson, Eric Feczko"
format: html
editor: visual
---

## Introduction

Often, whole-brain multi-variate prediction requires vast computational resources, lots of RAM, and/or high-performance computing (HPC). Here, we provide an example of whole-brain multi-variate prediction that can be run on 16GB of RAM with 4 CPUs. Throughout, we will show how to adopt this example to answer your questions your way.

## Step 1. Loading libraries

The first step is to load a series of libraries (see \[Module 3 RStudio Setup\](<https://github.com/DCAN-Labs/HDCC_Sandbox_tutorials/blob/main/examples/install_dependencies/HDCC_workshop_tutorial_package_script.R>) script for documentation on the function of each of these packages).

```{r}
#| echo: false
#| warning: false

library(arrow)
library(cifti)
library(data.table)
library(dplyr)
library(ggplot2)
library(ggsci)
library(lme4)
library(lmerTest)
library(nlme)
library(plotrix)
library(pls)
library(reshape2)
library(RSpectra)
library(tidyr)
```

## Step 2. Generating Functions to use.

The next step will define the individual functions used for this tutorial.

```{r}
#| echo: false
#| warning: false

#| Function 1: align_df_to_ids
#| This function appends a set of subject IDs to a data frame as the column named in "id_col"
align_df_to_ids <- function(df, ids, id_col = "id") {
  ids <- as.character(ids)
  df[[id_col]] <- as.character(df[[id_col]])

  missing <- setdiff(ids, df[[id_col]])
  if (length(missing) > 0) {
    stop(sprintf(
      "[FATAL] %d ids not present in df$%s. Examples: %s",
      length(missing), id_col, paste(head(missing, 10), collapse = ", ")
    ))
  }

  df2 <- df %>% slice(match(ids, .data[[id_col]]))

  if (!identical(df2[[id_col]], ids)) {
    stop("[FATAL] align_df_to_ids(): id alignment failed.")
  }
  df2
}

#| Function 2: align_rows_to_ids
#| This function ensures that rows within a matrix are aligned to the matrix X
align_rows_to_ids <- function(X, ids) {
  ids <- as.character(ids)
  rn <- rownames(X)

  if (is.null(rn)) stop("[FATAL] align_rows_to_ids(): X has NULL rownames.")
  rn <- as.character(rn)

  missing <- setdiff(ids, rn)
  if (length(missing) > 0) {
    stop(sprintf(
      "[FATAL] %d ids not present in rownames(X). Examples: %s",
      length(missing), paste(head(missing, 10), collapse = ", ")
    ))
  }

  X2 <- X[match(ids, rn), , drop = FALSE]

  if (!identical(rownames(X2), ids)) {
    stop("[FATAL] align_rows_to_ids(): rowname alignment failed.")
  }
  X2
}

#| Function 3: CheckCIFTI
#| This function checks a CIFTI file for NaNs and reports on the number found.
CheckCIFTI <- function(pconndir,pconn) {
  pconnpath <- paste(pconndir,"/",pconn,sep="")
  ciftidata <- read_cifti(pconnpath)
  cmat <- ciftidata$data
  cmat_nans <- sum(is.na(cmat))
  outputdf <- data.frame(pconn_name = pconn, number_nans = cmat_nans)
  return(outputdf)
}

#| Function 4: CommunityGridInfo
#| This function identifies the row min and row max for each community for a matrix given a set of community assignments in a data frame.
CommunityGridInfo <- function(community_df) {
  communities <- unique(community_df$comm)
  t(sapply(communities,function(x) {c(x,min(community_df$index[community_df$comm==x]),max(community_df$index[community_df$comm==x]))}))
}

##Extract subject ID extracts the subject ID from a path variable
extract_sub_id <- function(paths) sub(".*/sub-([^/]+)/.*", "\\1", paths)

#| Function 5: FCMap
#| This function produces a heatmap visualization of a correlation or statistic matrix organized and labeled by community structure.
FCMap <- function(cmat,plottitle='Correlation Matrix',negmax=-0.5,posmax=1,xlabel="ROI",ylabel="ROI",commcolor='black',comms_df) {
  cmat_nanzero <- cmat
  cmat_nanzero[is.na(cmat_nanzero)] <- 0
  cmat_long <- melt(cmat_nanzero)
  ggplot(cmat_long, aes(x = Var1, y = Var2, fill = value)) +
    geom_raster() +
    geom_hline(yintercept=comms_df$comm_min,color = commcolor) +
    geom_hline(yintercept=comms_df$comm_max,color = commcolor) +
    geom_vline(xintercept=comms_df$comm_min,color = commcolor) +
    geom_vline(xintercept=comms_df$comm_max,color = commcolor) +
    scale_y_continuous(breaks=round((comms_df$comm_min + comms_df$comm_max)/2),labels=comms_df$labels) +
    scale_x_continuous(breaks=round((comms_df$comm_min + comms_df$comm_max)/2),labels=comms_df$labels) +
    scale_fill_gsea(limits = c(negmax,posmax)) +
    coord_equal() +
    theme_minimal() +
    theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1)) +
    labs(title = plottitle, x = xlabel, y = ylabel)
}

#| Function 6: make_p
#| This function constructs a phenotype data frame from phenotypes loaded from a file, session and ids are used to match what is in the phenotype file to the selected ids and sessions.
make_p <- function(phenos, session, ids) {
  out <- phenos %>%
    filter(session_id == session) %>%
    select(-session_id) %>%
    mutate(id = sub("^sub-", "", participant_id)) %>%
    filter(id %in% ids) %>%
    select(-participant_id)

  # enforce unique id rows (if duplicates exist, you must resolve upstream)
  if (anyDuplicated(out$id)) {
    dup <- out$id[duplicated(out$id)]
    stop(sprintf(
      "[FATAL] Duplicated IDs in phenos for session %s. Examples: %s",
      session, paste(head(unique(dup), 10), collapse = ", ")
    ))
  }

  out
}

#| Function 7: make_x
#| This function constructs a flattened 2D matrix from correlation matrices. The upper triangular part is used to flatten the matrix into a cases X correlation data matrix.
make_X <- function(paths,datatype = 'pconn') {
  ids <- extract_sub_id(paths)

  if(datatype == "pconn"){
    X <- do.call(rbind, lapply(paths, pconnFunc))
  }
  if(datatype =="tsv"){
    X <- do.call(rbind, lapply(paths, tsvFunc))
  }
  rownames(X) <- ids

  # sanity checks
  stopifnot(nrow(X) == length(ids))
  stopifnot(identical(rownames(X), ids))

  X
}

#| Function 8: ManPlot
#| This function constructs manhattan plots to visualize significant findings grouped by community or communityXcommunity in the case of correlations
ManPlot <- function(V,
                    predictor.names = NULL,
                    group.structure = NULL,
                    specific.groups = NULL,
                    exclude.groups = NULL,
                    man.thresh = 0,
                    special.colors = NULL,
                    optional.index = NULL,
                    point.size = 1.5,
                    out.prefix = "Manhattan_Vector",
                    out.dir = ".",
                    width = 1600,
                    height = 900,
                    dpi = 200) {

  # ---- checks ----
  V <- as.matrix(V)
  p <- nrow(V)
  nvec <- ncol(V)

  if (is.null(predictor.names)) predictor.names <- paste0("X", seq_len(p))
  if (length(predictor.names) != p) stop("predictor.names must have length p (= nrow(V)).")

  if (is.null(group.structure)) group.structure <- rep("group1", p)
  if (length(group.structure) != p) stop("group.structure must have length p (= nrow(V)).")

  # ---- index handling (FIXED) ----
  if (is.null(optional.index)) {
    index <- seq_len(p)
  } else {
    if (length(optional.index) != p) stop("Specify same number of indices as predictors (length p).")
    index <- optional.index
  }

  # ---- colors ----
  dfcolor <- NULL
  if (!is.null(special.colors)) {
    # Expect special.colors as a 2-col object: group, color
    dfcolor <- as.data.frame(special.colors, stringsAsFactors = FALSE)
    if (ncol(dfcolor) != 2) stop("special.colors must have 2 columns: group, color.")
    colnames(dfcolor) <- c("group", "color")
    dfcolor$group <- as.factor(dfcolor$group)
  }

  # ---- requires ----
  if (!requireNamespace("dplyr", quietly = TRUE)) stop("Please install 'dplyr'.")
  if (!requireNamespace("ggplot2", quietly = TRUE)) stop("Please install 'ggplot2'.")
  if (!requireNamespace("ggtext", quietly = TRUE)) stop("Please install 'ggtext'.")
  if (!requireNamespace("forcats", quietly = TRUE)) stop("Please install 'forcats'.")

  # ---- iterate vectors ----
  for (i in seq_len(nvec)) {

    df <- data.frame(
      pred  = predictor.names,
      group = as.factor(group.structure),
      index = index,
      stringsAsFactors = FALSE
    )

    # subset groups if requested
    if (!is.null(specific.groups)) df <- dplyr::filter(df, group %in% specific.groups)
    if (!is.null(exclude.groups))  df <- dplyr::filter(df, !group %in% exclude.groups)

    # keep colors aligned to filtered groups
    dfcolor_i <- dfcolor
    if (!is.null(dfcolor_i)) {
      if (!is.null(specific.groups)) dfcolor_i <- dplyr::filter(dfcolor_i, group %in% specific.groups)
      if (!is.null(exclude.groups))  dfcolor_i <- dplyr::filter(dfcolor_i, !group %in% exclude.groups)
    }

    # values
    df$V <- abs(V[, i])

    # order within group by index, then build cumulative x-axis
    df <- df %>%
      dplyr::group_by(group) %>%
      dplyr::arrange(index, .by_group = TRUE) %>%
      dplyr::mutate(newindx = dplyr::row_number()) %>%
      dplyr::ungroup()

    df2 <- df %>%
      dplyr::group_by(group) %>%
      dplyr::summarise(max_idx = max(newindx), .groups = "drop") %>%
      dplyr::mutate(idx_add = dplyr::lag(cumsum(max_idx), default = 0)) %>%
      dplyr::select(group, idx_add)

    plot_data <- df %>%
      dplyr::inner_join(df2, by = "group") %>%
      dplyr::mutate(idx_cum = newindx + idx_add)

    # default colors if none supplied
    if (is.null(dfcolor_i)) {
      # alternating two colors
      groups <- levels(plot_data$group)
      dfcolor_i <- data.frame(
        group = factor(groups, levels = groups),
        color = rep(c("#276FBF", "#183059"), length.out = length(groups)),
        stringsAsFactors = FALSE
      )
    } else {
      # ensure all groups present
      dfcolor_i$group <- factor(dfcolor_i$group)
      # If user omitted some groups, fill with alternating defaults
      missing_groups <- setdiff(levels(plot_data$group), as.character(dfcolor_i$group))
      if (length(missing_groups) > 0) {
        add <- data.frame(
          group = factor(missing_groups, levels = levels(plot_data$group)),
          color = rep(c("#276FBF", "#183059"), length.out = length(missing_groups)),
          stringsAsFactors = FALSE
        )
        dfcolor_i <- dplyr::bind_rows(dfcolor_i, add)
      }
      # align factor levels
      dfcolor_i$group <- factor(dfcolor_i$group, levels = levels(plot_data$group))
    }

    axis_set <- plot_data %>%
      dplyr::group_by(group) %>%
      dplyr::summarise(center = mean(idx_cum), .groups = "drop") %>%
      dplyr::left_join(dfcolor_i, by = "group")

    ylim <- 1.2 * max(plot_data$V, na.rm = TRUE)

    gg_plot_title <- paste0("Manhattan Vector ", i)  # (FIXED)

    manhplot <- ggplot2::ggplot(
      data = plot_data,
      mapping = ggplot2::aes(x = idx_cum, y = V, color = forcats::as_factor(group))
    ) +
      ggplot2::geom_point(alpha = 0.75, size = point.size) +
      ggplot2::scale_x_continuous(label = axis_set$group, breaks = axis_set$center) +
      ggplot2::scale_y_continuous(expand = c(0, 0), limits = c(0, ylim)) +
      ggplot2::scale_color_manual(values = axis_set$color) +
      ggplot2::labs(x = NULL, y = "Absolute Value \nEigenvector \nLoadings") +
      ggplot2::ggtitle(gg_plot_title) +
      ggplot2::theme_minimal() +
      ggplot2::theme(
        legend.position = "none",
        panel.grid.major.x = ggplot2::element_blank(),
        panel.grid.minor.x = ggplot2::element_blank(),
        axis.title.y = ggtext::element_markdown(),
        axis.text.x = ggplot2::element_text(angle = 60, size = 6, vjust = 0.5)
      )

    if (man.thresh > 0) {
      manhplot <- manhplot +
        ggplot2::geom_hline(yintercept = man.thresh, color = "red", linetype = "solid")
    }

    # ---- save ----
    if (!dir.exists(out.dir)) dir.create(out.dir, recursive = TRUE)
    fname <- file.path(out.dir, sprintf("%s_%d.png", out.prefix, i))
    ggplot2::ggsave(filename = fname, plot = manhplot, width = width / dpi, height = height / dpi, dpi = dpi)

    # also print to current device (optional)
    print(manhplot)
  }

  invisible(TRUE)
}

#| Function 9: pconnFunc
#| This function loads a pconn and converts it into a vector. If dontcheckROI is set to false, it will instead report the number of ROIs.
pconnFunc <- function(path,dontcheckROIs = TRUE){
  pconn <- cifti::read_cifti(path)
  mat <- pconn$data
  if (dontcheckROIs) {
    vec <- mat[upper.tri(mat, diag = FALSE)]
    vec
  } else
  {
    vec <- dim(mat[1])
    vec
  }
}

#| Function 10: ReshapeVectorAsMatrix
#| This function reforms a vector into the proper matrix format. The matlength parameter specifies the number of ROIs. The diagval parameter imposes the value (default = 1) set on a diagonal.
ReshapeVectorAsMatrix <- function(dummy_vec,matlength,diagval=1) {
  dummy_emptymat = matrix( data = rep(0,matlength^2),nrow = matlength, ncol = matlength)
  dummy_emptymat[upper.tri(dummy_emptymat,diag = FALSE)] <- dummy_vec
  diag(dummy_emptymat) <- diagval
  dummy_transpose <- t(dummy_emptymat)
  dummy_transpose[upper.tri(dummy_transpose)] <- dummy_vec
  return(dummy_transpose)
}

#| Function 11: ReshapeWeightsAsMatrices
#| This function reshapes a set of parameter estimates into a correlation matrix.
ReshapeWeightsAsMatrices <- function(weightarray,matlength,usable_cols = NULL) {
  if (is.null(usable_cols)){
    temp_weightarray <- weightarray
  } else
  {
    temp_weightarray <- matrix(data = NA, nrow = length(usable_cols), ncol = dim(weightarray)[2])
    temp_weightarray[usable_cols,] = weightarray
  }
  weightindex <- 1
  weightlimit <- dim(temp_weightarray)[2]
  weightlist <- vector("list", weightlimit)
  while(weightindex <= weightlimit) {
      weightlist[[weightindex]] <- ReshapeVectorAsMatrix(temp_weightarray[,weightindex],matlength)
      weightindex <- weightindex + 1
  }
  return(weightlist)
}

#| Function 12: right_rows
#| This function ensures that the times, ids, and data points match with the underlying data, ensuring that only the rows used for analysis are selected.
right_rows <- function (data, times, ids, Q_points) {
    fids <- factor(ids, levels = unique(ids))
    if (!is.list(Q_points))
        Q_points <- split(Q_points, row(Q_points))
    ind <- mapply(findInterval, Q_points, split(times, fids))
    ind[ind < 1] <- 1
    rownams_id <- split(row.names(data), fids)
    ind <- mapply(`[`, rownams_id, split(ind, col(ind)))
    data[c(ind), ]
}

#| Function 13: tsvFunc
#| This function is the equivalent of pconnFunc except it operates on the tsv files. dontcheckROIs, when set to FALSE, will report the number of ROIs.
tsvFunc <- function(path,dontcheckROIs = TRUE){
  tsv <- read.table(path,header=TRUE)
  mat <- as.matrix(tsv[,-1])
  if (dontcheckROIs) {
    vec <- mat[upper.tri(mat, diag = FALSE)]
    vec <- as.numeric(vec)
    vec
  } else
  {
    vec <- dim(mat)[1]
    vec
  }
}

#| Function 14: WritePCOutputs
#| This function takes the output weight matrices and produces tsvs
WritePCOutputs <- function(weightmatlist,fileroot = "PC_weights_for_",filepath,defaultNA=0) {
  for(varindex in 1:length(weightmatlist)){ 
    temp_mat <- weightmatlist[[varindex]]
    temp_mat[is.na(temp_mat)] <- defaultNA
    temp_vec <- rowSums(temp_mat,na.rm = TRUE)
    temp_mat_filename <- paste(filepath,"/",fileroot,"_PC",as.character(varindex),".tsv",sep="")
    print(temp_mat_filename)
    write.table(temp_mat,file = temp_mat_filename,col.names = FALSE, row.names = FALSE)
    temp_vec_filename <- paste(filepath,"/",fileroot,"_ROI-sum-weight_PC",as.character(varindex),".tsv",sep="")
    print(temp_vec_filename)
    write.table(temp_vec,file = temp_vec_filename,col.names = FALSE, row.names = FALSE)
  }
}

#| Function 15: ylmepred
#| This function uses a created linear-mixed effects (LME) model and newdata to predict the outcome variable. The LME model can be extended to predict data in subsequent timepoints or ages.
ylmepred <- function (lmeObject, newdata, timeVar, times = NULL, M = 200L, 
  interval = c("confidence", "prediction"), all_times = FALSE, 
  level = 0.95, return_data = FALSE, seed = 1L) 
{
  if (!inherits(lmeObject, "lme") && !inherits(lmeObject, 
    "lmeComponents")) 
    stop("Use only with 'lme' or 'lmeComponents' objects.\n")
  interval <- match.arg(interval)
  if (inherits(lmeObject, "lme")) {
    data <- lmeObject$data
    formYx <- formula(lmeObject)
    mfX <- model.frame(terms(formYx), data = data)
    TermsX <- attr(mfX, "terms")
    formYz <- formula(lmeObject$modelStruct$reStruct[[1]])
    mfZ <- model.frame(terms(formYz), data = data)
    TermsZ <- attr(mfZ, "terms")
    idVar <- names(lmeObject$modelStruct$reStruct)
    betas <- fixef(lmeObject)
    sigma <- lmeObject$sigma
    D <- lapply(pdMatrix(lmeObject$modelStruct$reStruct), 
      "*", sigma^2)[[1]]
    V <- vcov(lmeObject)
    times_orig <- data[[timeVar]]
    times_orig <- times_orig[!is.na(times_orig)]
  }
  else {
    formYx <- lmeObject$formYx
    TermsX <- lmeObject$TermsX
    formYz <- lmeObject$formYz
    TermsZ <- lmeObject$TermsZ
    idVar <- lmeObject$idVar
    betas <- lmeObject$betas
    sigma <- lmeObject$sigma
    D <- lmeObject$D
    V <- lmeObject$V
    times_orig <- lmeObject$times_orig
  }
  all_vars <- unique(c(all.vars(TermsX), all.vars(TermsZ)))
  newdata_nomiss <- newdata[complete.cases(newdata[all_vars]), 
    ]
  mfX_new <- model.frame(TermsX, data = newdata_nomiss)
  X_new <- model.matrix(formYx, mfX_new)
  mfZ_new <- model.frame(TermsZ, data = newdata_nomiss)
  Z_new <- model.matrix(formYz, mfZ_new)
  na_ind <- attr(mfX_new, "na.action")
  y_new <- model.response(mfX_new, "numeric")
  if (length(idVar) > 1) 
    stop("the current version of the function only works with a single grouping variable.\n")
  if (is.null(newdata[[idVar]])) 
    stop("subject id variable not in newdata.")
  id_nomiss <- match(newdata_nomiss[[idVar]], unique(newdata_nomiss[[idVar]]))
  n <- length(unique(id_nomiss))
  modes <- matrix(0, n, ncol(Z_new))
  post_vars <- DZtVinv <- vector("list", n)
  for (i in seq_len(n)) {
    id_i <- id_nomiss == i
    X_new_id <- X_new[id_i, , drop = FALSE]
    Z_new_id <- Z_new[id_i, , drop = FALSE]
    Vi_inv <- solve(Z_new_id %*% tcrossprod(D, Z_new_id) + 
      sigma^2 * diag(sum(id_i)))
    DZtVinv[[i]] <- tcrossprod(D, Z_new_id) %*% Vi_inv
    modes[i, ] <- c(DZtVinv[[i]] %*% (y_new[id_i] - X_new_id %*% 
      betas))
    t1 <- DZtVinv[[i]] %*% Z_new_id %*% D
    t2 <- DZtVinv[[i]] %*% X_new_id %*% V %*% crossprod(X_new_id, 
      Vi_inv) %*% Z_new_id %*% D
    post_vars[[i]] <- D - t1 + t2
  }
  fitted_y <- c(X_new %*% betas) + rowSums(Z_new * modes[id_nomiss, 
    , drop = FALSE])
  if (is.null(times) || !is.numeric(times)) {
    times <- seq(min(times_orig), max(times_orig), length.out = 100)
  }
  id <- match(newdata[[idVar]], unique(newdata[[idVar]]))
  last_time <- tapply(newdata[[timeVar]], id, max)
  times_to_pred <- lapply(last_time, function(t) if (all_times) 
    times
  else times[times > t])
  id_pred <- rep(seq_len(n), sapply(times_to_pred, length))
  newdata_pred <- right_rows(newdata, newdata[[timeVar]], 
    id, times_to_pred)
  newdata_pred[[timeVar]] <- unlist(times_to_pred)
  mfX_new_pred <- model.frame(TermsX, data = newdata_pred, 
    na.action = NULL)
  X_new_pred <- model.matrix(formYx, mfX_new_pred)
  mfZ_new_pred <- model.frame(TermsZ, data = newdata_pred, 
    na.action = NULL)
  Z_new_pred <- model.matrix(formYz, mfZ_new_pred)
  predicted_y <- c(X_new_pred %*% betas) + rowSums(Z_new_pred * 
    modes[id_pred, , drop = FALSE])
  return(list(fit=fitted_y, pred=predicted_y))
}
```

## Step 3. Selecting data files

The next step will select the data files we will want to use for generating the longitudinal model. These can be anything, as long as specific lines are edited.

### 1) Selecting imaging files

Change ROOT to the path where the pipeline derivatives are located (e.g. `XCP_D`). Change pconnname to the root for the imaging files you want to load (e.g. `task-rest_space-fsLR_seg-Gordon_stat-pearsoncorrelation_relmat`). Change pconnpattern to select the imaging file types you want to load (.e.g `.tsv`). For example if you wanted to load pconns, you would change the extension from tsv to pconn.nii.

For HBCD we will need to aggregate across two output flders: xcp_d-0f306a2f+0ef9c88a is better for V02, while xcp_d-2afa9081+0ef9c88a is better for V03 and V04.

For shortened workshops, we can skip this step as it is time consuming.

```{r}
#| eval: false
#| echo: false

#The `ROOT` paths in the first code chunk, which is reprinted below. `V2ROOT` may be needed if you are using data from more than one derivative folder.

#ROOT <- "/shared/hackathon/hbcd/v2.0/hbcd/derivatives/xcp_d-2afa9081+0ef9c88a"
#V2ROOT <- "/shared/hackathon/hbcd/v2.0/hbcd/derivatives/xcp_d-0f306a2f+0ef9c88a"
## ------------------------------------------------------------
## 1. Get subject directories
## ------------------------------------------------------------
#subs <- list.dirs(
#  path        = ROOT,
#  full.names  = TRUE,
#  recursive   = FALSE
#)

#v2subs <- list.dirs(
#  path        = V2ROOT,
#  full.names  = TRUE,
#  recursive   = FALSE
#)


# Keep only directories that start with "sub-"
#subs <- subs[grepl("^sub-", basename(subs))]
#v2subs <- v2subs[grepl("^sub-", basename(v2subs))]

#To select a different imaging file, edit the `pconnname` below.
#pconnname <- "task-rest_space-fsLR_seg-Gordon_stat-pearsoncorrelation_relmat"

#cat("Number of subject directories found:", length(subs), "\n")

## ------------------------------------------------------------
## 2. Get all files recursively within each subject
## ------------------------------------------------------------
#sessions <- list.files(
#  path       = subs,
#  recursive  = FALSE,
#  full.names = TRUE
#)

#v2sessions <- list.files(
#  path       = v2subs,
#  recursive  = FALSE,
#  full.names = TRUE
#)
#cat("Total sessions found:", length(sessions), "\n")
#cat("Total sessions found for V02 processing:", length(v2sessions), "\n")

#head(sessions)
#head(v2sessions)

#pconnpattern = paste(pconnname,".tsv",sep="")
#pconn_files <- list.files(
#  path       = sessions,
#  pattern    = pconnpattern,
#  recursive  = TRUE,
#  full.names = TRUE
#)
#v2pconn_files <- list.files(
#  path       = v2sessions,
#  pattern    = pconnpattern,
#  recursive  = TRUE,
#  full.names = TRUE
#)

#cat("Total pconn files found:", length(pconn_files), "\n")

#cat("Total pconn files found for v2 processing:", length(v2pconn_files), "\n")

#subject_ids <- sub(".*(sub-[^/]+).*", "\\1", pconn_files)
#subject_ids_clean <- sub(".*sub-([^_]+)_ses.*", "\\1", subject_ids)

#ses_id <- sub(".*_(ses-[^_]+)_.*", "\\1", subject_ids)
#head(ses_id)

#v2subject_ids <- sub(".*(sub-[^/]+).*", "\\1", v2pconn_files)
#v2subject_ids_clean <- sub(".*sub-([^_]+)_ses.*", "\\1", v2subject_ids)

#v2ses_id <- sub(".*_(ses-[^_]+)_.*", "\\1", v2subject_ids)
#head(v2ses_id)
```

### 2) Bin imaging data into session visits

The next lines will organize our selected imaging files into the different session visits (e.g. V02, V03, V04)

```{r}
#| eval: false
#| echo: false
#ses_V02 <- v2pconn_files[grepl("_ses-V02", basename(v2pconn_files))]
#sub_ids_V02 <- sub(".*/sub-([^/]+)/.*", "\\1", ses_V02)
#ses_V03 <- pconn_files[grepl("_ses-V03", basename(pconn_files))]
#sub_ids_V03 <- sub(".*/sub-([^/]+)/.*", "\\1", ses_V03)
#ses_V04 <- pconn_files[grepl("_ses-V04", basename(pconn_files))]
#sub_ids_V04 <- sub(".*/sub-([^/]+)/.*", "\\1", ses_V04)

```

### 3a) Identify common participants

The next lines will identify the common participants across all sessions. It will also save the intermediate output to avoid having to do this later. Please make sure this output remains in the sandbox or on a NIST compliant platform.

```{r}
# common_ids <- Reduce(
#   union,
#   list(sub_ids_V02, sub_ids_V03)
# )

#saveRDS(common_ids,"~/common.RDS")
```

### 3b) load preexisting common IDS

If running the final example, these intermediates may already exist, and this code block can be run instead.

```{r}
common_ids <- readRDS("/shared/hackathon/working-area/xcpd_prediction/common.RDS")

```

### 3c) check IDs

This code block just prints the length and first few rows of the common IDs to sanity check them.

```{r}
length(common_ids)
head(common_ids)
```

### 4) Load phenotypic data

The next section loads the phenotypic (i.e. non-imaging ) data. Choosing a different "phenofolder" and "phenofile" will enable users to use different phenotypic data available for HBCD. Change the `phenofolder` to select a different dataset. Change the `phenofile` to select a different tabulated file.

```{r}
#| echo: false

phenofolder <- "/shared/hackathon/hbcd/v1.1/hbcd/rawdata/phenotype"
phenofile <- paste(phenofolder,"sed_bm_strsup.parquet",sep = "/")
phenos <- read_parquet(phenofile)
```

### 5) Identify missingness in data

The next section produces a table to evaluate what data may be missing as organized by session.

```{r}
#| echo: false
pheno_vars <- setdiff(names(phenos), c("participant_id", "session_id"))

na_table <- phenos %>%
  group_by(session_id) %>%
  summarise(
    across(
      all_of(pheno_vars),
      ~ sum(!is.na(.)),
      .names = "{.col}"
    ),
    .groups = "drop"
  )

na_table_t <- na_table %>%
  pivot_longer(
    -session_id,
    names_to = "variable",
    values_to = "n_non_missing"
  ) %>%
  pivot_wider(
    names_from = session_id,
    values_from = n_non_missing
  )

na_table_t

```

## Step 4. Prepare imaging data.

The next step is to prepare the imaging data by loading it into R. This includes combining our imaging data with the phenotypic data and ensuring the data are aligned and checked for missingness.

### 1a) Build X matrices

These commands will make the imaging matrices from the tsv files identified in Step 3. If this has already been done, intermediate files can be loaded instead.

```{r}
#| warning: false


#options(stringsAsFactors = FALSE)
# X0 <- make_X(ses_V02,"tsv")
# X2 <- make_X(ses_V03,"tsv")
 #X4 <- make_X(ses_V04,"tsv")
```

### 1b) Clean and save imaging data for later use

First-pass cleaning restricts imaging data to your current common_ids. Keeps only IDs that appear in the pconn matrices, and saves intermediate data.

```{r}
#| warning: false
 
# X0 <- X0[rownames(X0) %in% common_ids, , drop = FALSE]
# X2 <- X2[rownames(X2) %in% common_ids, , drop = FALSE]
# X4 <- X4[rownames(X4) %in% common_ids, , drop = FALSE]
# saveRDS(X0,"~/X0.RDS")
# saveRDS(X2,"~/X2.RDS")
# saveRDS(X4,"X4.RDS")
```

### 1c) Load intermediate clean files.

Alternatively if data already exist, load the intermediate files instead of generating them above. This skips the time consuming data generation process.

```{r}
#| warning: false

 X0 <- readRDS("/shared/hackathon/working-area/xcpd_prediction/X0.RDS")
 X2 <- readRDS("/shared/hackathon/working-area/xcpd_prediction/X2.RDS")
# X4 <- readRDS("/shared/hackathon/working-area/xcpd_prediction/X4.RDS")
```

### 1c) missing data

In order to perform dimensionality reduction we will need to remove any matrices with missing data. This section checks for rows and columns to remove data. It is highly recommended to adjust the values in here for your question.

```{r}
#| warning: false
 usable_x0_rows <- rowSums(is.na(X0)) <= 993
 missing_x0_rows <- rowSums(is.na(X0)) > 993
 X0 <- X0[usable_x0_rows,]
 missing_x0_cols <- colSums(is.na(X0)) > 0
 usable_x0_cols <- colSums(is.na(X0)) == 0
 
 usable_x2_rows <- rowSums(is.na(X2)) == 0
 missing_x2_rows <- rowSums(is.na(X2)) > 0
 X2 <- X2[usable_x2_rows,]
 missing_x2_cols <- colSums(is.na(X2)) > 0
 usable_x2_cols <- colSums(is.na(X2)) == 0
 
 usable_cols <- (usable_x2_cols*usable_x0_cols == 1)
 missing_cols <- (usable_x2_cols*usable_x0_cols == 0)
 X0 <- X0[,usable_cols]
 X2 <- X2[,usable_cols]
 
```

### 1e) scale matrices

In order to perform dimensionality reduction we will first need to scale the matrices. This is better to do prior to filtering so that we can leverage as much data as possible. We should also remove any matrices with missing data.

```{r}
#| warning: false
 X0 <- scale(X0)
 X2 <- scale(X2)
# X4 <- scale(X4)
```

### 2) Determine number of ROIs

Load an example file so we know the number of ROIs(ensures we can accurately retrieve the matrix and visualize).

```{r}
#| warning: false

#nROIs <-  pconnFunc(ses_V02[1],dontcheckROIs=FALSE)
#nROIs <-  tsvFunc(ses_V02[1],dontcheckROIs=FALSE)
nROIs <- 333
```

### 3) Load phenos and compute FINAL common_ids intersection

Here we load the phenotypic data and make sure that all phenotypic and imaging data align with the common IDs identified previously. This ensures IDs exist across ALL data.

```{r}
#| warning: false

phenos <- read_parquet(phenofile) %>%
  dplyr::select(
    sed_bm_strsup_adjusted_age,
    sed_bm_strsup_scale_score,
    participant_id,
    session_id
  )

p0 <- make_p(phenos, "ses-V02", common_ids)
p2 <- make_p(phenos, "ses-V03", common_ids)
#p4 <- make_p(phenos, "ses-V04", common_ids)

common_p0_ids <- Reduce(
  intersect,
  list(p0$id, rownames(X0))
)
common_p2_ids <- Reduce(
  intersect,
  list(p2$id, rownames(X2))
)

#common_p4_ids <- Reduce(
#  intersect,
#  list(p4$id, rownames(X4))
#)

all_usable_ids <- Reduce(
  union,
  list(common_p0_ids,common_p2_ids)
)
common_ids <- Reduce(
  intersect,
  list(common_p0_ids,common_p2_ids)
)
unique_ids <- Reduce(
  setdiff,
  list(all_usable_ids,common_ids)
)
cat("[INFO] length(all_usable_ids) =", length(all_usable_ids), "\n")
cat("[INFO] head(all_usable_ids) =", paste(head(all_usable_ids), collapse = ", "), "\n")
cat("[INFO] length(common_ids) =", length(common_ids), "\n")
cat("[INFO] head(common_ids) =", paste(head(common_ids), collapse = ", "), "\n")
cat("[INFO] length(unique_ids) =", length(unique_ids), "\n")
cat("[INFO] head(unique_ids) =", paste(head(unique_ids), collapse = ", "), "\n")

```

### 4) NOW enforce canonical ordering everywhere, via common_ids.

Using the common_ids as the ordering reference, enforce the same order through all data ensuring alignment of imaging and phenotypic data.

```{r}
#| warning: false

# Align X matrices to common_ids order

X0 <- align_rows_to_ids(X0, common_p0_ids)
X2 <- align_rows_to_ids(X2, common_p2_ids)
#X4 <- align_rows_to_ids(X4, common_p4_ids)

# Rebuild p0/p2/p4 on FINAL common_ids, then align order
p0 <- make_p(phenos, "ses-V02", common_p0_ids) %>% align_df_to_ids(common_p0_ids)
p2 <- make_p(phenos, "ses-V03", common_p2_ids) %>% align_df_to_ids(common_p2_ids)
#p4 <- make_p(phenos, "ses-V04", common_p4_ids) %>% align_df_to_ids(common_p4_ids)
```

### 5) Final sanity checks, and make temp table for debugging.

These last few checks ensure that the data are truly cleaned and ready for analysis.

```{r}
#| warning: false
stopifnot(identical(rownames(X0), common_p0_ids))
stopifnot(identical(rownames(X2), common_p2_ids))
#stopifnot(identical(rownames(X4), common_p4_ids))
stopifnot(identical(p0$id, common_p0_ids))
stopifnot(identical(p2$id, common_p2_ids))
#stopifnot(identical(p4$id, common_p4_ids))

#this doesn't make sense unless you're checking for completeness
#temp <- data.frame(
#  rownames_X0 = rownames(X0),
#  rownames_X2 = rownames(X2),
#  rownames_X4 = rownames(X4),
#  common_ids  = all_usable_ids,
#  p0_id       = p0$id,
#  p2_id       = p2$id,
#  p4_id       = p4$id,
#  stringsAsFactors = FALSE
#)

cat("[INFO] Alignment checks passed. total rows =", nrow(p0)+nrow(p2), "\n")
```

### 6) Add median time variable to phenotypes, in case one is needed.

A categorical or ordinal time variable may be needed for some analyses. This code adds such a variable into the model. To change the values, simply manipulate the numbers below.

```{r}
#| echo: false
p0$time <- 6
p2$time <- 24
#p4$time <- 52
colnames(p0) <- c("age","y", "id", "time")
colnames(p2) <- c("age","y", "id", "time")
#colnames(p4) <- c("age","y", "id", "time")

```

## Step 5. Prepare data for model training.

The next step will split our imaging data and perform dimensionality reduction, according to good standards and practices. The default imaging data used will be the Gordon parcellated connectivity matrices in tsv form.

### 1) Get unique IDs

Pull all the unique IDs using the common_ids variable

```{r}
#| echo: false

set.seed(123)  # reproducibility

length(all_usable_ids)
length(unique_ids)
length(common_ids)
```

### 2) Split data into train and test via holdout

Randomly select 306 unique and 28 common IDs for training (90 percent of independent cases), change the number for training by editing size for each sample below.

```{r}
#| echo: false
train_unique_ids <- sample(unique_ids, size = 306, replace = FALSE)
train_common_ids <- sample(common_ids,size = 28, replace = FALSE)
train_ids <- union(train_unique_ids,train_common_ids)
```

### 3) Create test data.

Remaining cases go to the test dataset.

```{r}
test_ids <- setdiff(all_usable_ids, train_ids)

length(train_ids)  
length(test_ids)


```

### 4) Calculate Singular Value Decomposition

This must be calculated separately for each wave as well as splitting and test and train to avoid data leakage. Make sure the matrices are scaled prior to running this step.

```{r}
#| echo: false


x0train <- X0[rownames(X0) %in% train_ids, , drop = FALSE]
x0test <- X0[!(rownames(X0) %in% train_ids), , drop = FALSE]
xmeans <- colMeans(x0train)
x0train <- t(apply(x0train, 1, function(x) x-xmeans))
x0test <- t(apply(x0test, 1, function(x) x-xmeans))

x2train <- X2[rownames(X2) %in% train_ids, , drop = FALSE]
x2test <- X2[!(rownames(X2) %in% train_ids), , drop = FALSE]
xmeans <- colMeans(x2train)
x2train <- t(apply(x2train, 1, function(x) x-xmeans))
x2test <- t(apply(x2test, 1, function(x) x-xmeans))

#x4train <- X4[rownames(X4) %in% train_ids, , drop = FALSE]
#x4test <- X4[!(rownames(X4) %in% train_ids), , drop = FALSE]
#xmeans <- colMeans(x4train)
#x4train <- t(apply(x4train, 1, function(x) x-xmeans))
#x4test <- t(apply(x4test, 1, function(x) x-xmeans))
```

### 5) Extract principal components (PCs)

10 principal components from the imaging data for training and testing. This is done separately by session, and splitting train and test to avoid data leakage. Changing "k" on line 1092 changes how many PCs are selected.

```{r}
#| echo: false
k <- 10

sv0 <- svds(x0train, k=k, nu=k, nv=k)
pc0train <- x0train %*% as.matrix(sv0$v)
pc0test <- x0test %*% as.matrix(sv0$v)
y0train <- p0 %>% filter(id %in% rownames(pc0train))
colnames(pc0train) <- paste0("pc", 1:k)
y0test <- p0 %>% filter(id %in% rownames(pc0test))
colnames(pc0test) <- paste0("pc", 1:k)

sv2 <- svds(x2train, k=k, nu=k, nv=k)
pc2train <- x2train %*% as.matrix(sv2$v)
pc2test <- x2test %*% as.matrix(sv2$v)
y2train <- p2 %>% filter(id %in% rownames(pc2train))
colnames(pc2train) <- paste0("pc", 1:k)
y2test <- p2 %>% filter(id %in% rownames(pc2test))
colnames(pc2test) <- paste0("pc", 1:k)

#sv4 <- svds(x4train, k=k, nu=k, nv=k)
#pc4train <- x4train %*% as.matrix(sv4$v)
#pc4test <- x4test %*% as.matrix(sv4$v)
#y4train <- p4 %>% filter(id %in% rownames(pc4train))
#colnames(pc4train) <- paste0("pc", 1:k)
#y4test <- p4 %>% filter(id %in% rownames(pc4test))
#colnames(pc4test) <- paste0("pc", 1:k)
```

### 6) Data aggregation

PCs and phenotypic data are now combined across sessions into training and testing datasets for model training and testing.

```{r}
#| echo: false

ztrain <- rbind(pc0train, pc2train)
ytrain <- rbind(y0train,y2train)
data_train <- data.frame(ytrain, ztrain)

ztest <- rbind(pc0test, pc2test)
ytest <- rbind(y0test,y2test)
data_test <- data.frame(ytest, ztest)

str(sv0)
str(sv2)
#str(sv4)

```

## Step 6. Model training and prediction.

The next section will train and test Linear Mixed Effects Models using the parental stress variable as the outcome and the extracted PCs as predictor variables.

### 1) Clean data

First we must identify bad/missing data and remove any rows with missing or bad data.

```{r}
mf_vars <- c("y", "id", "time", paste0("pc", 1:10))

bad_counts <- sapply(data_train[, mf_vars, drop = FALSE], function(x) {
  if (is.numeric(x)) sum(!is.finite(x)) else sum(is.na(x))
})

bad_counts


```

### 2) Construct a linear mixed effects model (LME)

One can modify the statistical model used to perform BWAS via LME, which will use all 10 PCs with a PC1 X time interaction by default. Modify the `fixed` variable to select the fixed effects and interactions you want to model. Change the `random` variable to select the random effects and interactions to model. Change the `method` to use a different mixed-effects model estimator.

```{r}
model_1 <- nlme::lme(
  fixed  = y ~ pc1 + pc2 + pc3 + pc4 + pc5 + pc6 + pc7 + pc8 + pc9 + pc10 + time*pc1,
  random = ~ 1 | id,
  data   = data_train,
  method = "REML",
  na.action = na.omit
)

complete_data_test <- data_test[complete.cases(data_test),]
output <- ylmepred(model_1, complete_data_test, timeVar = "time", times = c(6,24) ,all_times = TRUE, seed = 1L)

```

### 3) Combine predicted outcomes with sessions and subjects

To combine these data, we construct a data frame to map predicted outcomes to sessions and subjects.

```{r}

nm <- names(output$fit)

nm_to_id <- unlist(lapply(nm,function(t) complete_data_test[["id"]][rownames(complete_data_test) == t]))
nm_to_time <- unlist(lapply(nm,function(t) complete_data_test[["time"]][rownames(complete_data_test) == t]))
df_ids <- data.frame(
  key  = nm,  # <-- keep original key
  ID   = nm_to_id,
  time = nm_to_time,
  stringsAsFactors = FALSE
)

df_ids$time <- as.integer(df_ids$time)

# map yhat by key (order-proof)
df_ids$yhat <- unname(output$fit[df_ids$key])

# optional
df_ids$key <- NULL
```

### 4) Combine observed with predicted outcomes.

Using IDs and the time variable we can map the data back to the unique subjects and sesions

```{r}
results <- complete_data_test %>%
  mutate(ID = id,
         time = as.integer(time),
         y=y) %>% 
  dplyr::select(ID, time, y) %>%
  inner_join(., df_ids, by=c("ID", "time"))
```

## Step 7. Results and visualizations

The next section shows results and performs data visualizations including prediction plots, manhattan plots, heatmaps, and outputting brain-based visualizations.

### 1) Compute model performnace

One way to compute model performance is to calculate the correlation between predicted and observed grouped by the time variable.

```{r}
r0 <- results %>% filter(time <= 12)
cor(r0$y, r0$yhat)
r2 <- results %>% filter(time > 12 & time <= 36)
cor(r2$y, r2$yhat)
#r4 <- results %>% filter(time > 36 && time <= 60)
#cor(r4$y, r4$yhat)
```

### 2) Plot wave 1 model performance

One such plot is a scatter plot of predicted vs. observed using ggplot2 for the first wave. A scatter plot of the predicted vs. observed outcomes is very helpful for evaluating model performance. Density heatmaps further help by revealing where the greatest concentration of cases are located. 

```{r}

ggplot(r0, aes(x = y, y = yhat)) +
  stat_density_2d(
    aes(fill = after_stat(level)),
    geom = "polygon",
    alpha = 0.4,
    contour = TRUE
  ) +
  scale_fill_viridis_c(option = "C", guide = "none") +

  geom_point(alpha = 0.4, size = 1) +

  geom_abline(
    slope = 1, intercept = 0,
    linetype = "dashed",
    color = "red",
    linewidth = 1
  ) +

  coord_equal() +

  labs(
    x = "Observed (y)",
    y = "Predicted (yhat)",
    title = "Observed vs Predicted",
    subtitle = "Red dashed line = 45° reference"
  ) +

  theme_minimal(base_size = 14)
```

### 3) Plot wave 2 model performance

One such plot is a scatter plot of predicted vs. observed using ggplot2 for wave 2.

```{r}

ggplot(r2, aes(x = y, y = yhat)) +
  stat_density_2d(
    aes(fill = after_stat(level)),
    geom = "polygon",
    alpha = 0.4,
    contour = TRUE
  ) +
  scale_fill_viridis_c(option = "C", guide = "none") +

  geom_point(alpha = 0.4, size = 1) +

  geom_abline(
    slope = 1, intercept = 0,
    linetype = "dashed",
    color = "red",
    linewidth = 1
  ) +

  coord_equal() +

  labs(
    x = "Observed (y)",
    y = "Predicted (yhat)",
    title = "Observed vs Predicted",
    subtitle = "Red dashed line = 45° reference"
  ) +

  theme_minimal(base_size = 14)
```

### 4) Plot wave 3 model performance

One such plot is a scatter plot of predicted vs. observed using ggplot2 for wave 3.

```{r}

#ggplot(r4, aes(x = y, y = yhat)) +
#  stat_density_2d(
#    aes(fill = after_stat(level)),
#    geom = "polygon",
#    alpha = 0.4,
#    contour = TRUE
#  ) +
#  scale_fill_viridis_c(option = "C", guide = "none") +

#  geom_point(alpha = 0.4, size = 1) +

#  geom_abline(
#    slope = 1, intercept = 0,
#    linetype = "dashed",
#    color = "red",
#    linewidth = 1
#  ) +

#  coord_equal() +

#  labs(
#    x = "Observed (y)",
#    y = "Predicted (yhat)",
#    title = "Observed vs Predicted",
#    subtitle = "Red dashed line = 45° reference"
#  ) +

#  theme_minimal(base_size = 14)
```

### 4) Load R data

Data within the examples folder must be loaded for heatmap visualizations, this contains ROI indices for ordering to the Gordon matrix. Other .Rdata files can be generated for other matrices to order them as well.

```{r}
load("~/HDCC_Sandbox_tutorials/examples/XCP_D_multivariate_prediction/ROI.RData")
ROIindex <- unique(ROI$roi1)
ROIcomm <- sapply( ROIindex ,function(x) {ROI$com1[ROI$roi1==x][1]} )
ROIdf <- data.frame(index = ROIindex, comm = ROIcomm)
ROIdf_cortical <- ROIdf[1:333,]
ROIdf_cortical_ordered <- ROIdf_cortical[order(ROIdf_cortical$comm),]
ROIdf_cortical_ordered$old_index <- ROIdf_cortical_ordered$index
ROIdf_cortical_ordered$index <- 1:333
```

### 5) Load community file to define grid lines and set organization.

The community file lists how the data are organized according to the Gordon community structure. Editing the Gordoncommfile variable below will allow someone to use a different community file. Only useful for heatmap visualizations.

```{r}
Gordoncommfile <- "~/HDCC_Sandbox_tutorials/examples/XCP_D_multivariate_prediction/gordon_communities_plus_subcortical.csv"
Gordoncomms <- read.csv(Gordoncommfile)

```

### 6) Reshape weight vectors back into appropriate matrices.

2D matrices are needed to visualize the heatmaps appropriately.

```{r}
sv0weightmatlist <- ReshapeWeightsAsMatrices(sv0$v,nROIs,usable_cols)
sv2weightmatlist <- ReshapeWeightsAsMatrices(sv2$v,nROIs,usable_cols)
#sv4weightmatlist <- ReshapeWeightsAsMatrices(sv4$v,nROIs)
```

### 7) Produce heatmap visualizations using the FCmap ( function 5 ) created above.

Parameters can be edited both in the FCmap function, as well as the parameters below. Such as the title through plottitle, and the positive and negative limits through posmax and negmax respectively.

```{r}
#heatmap visualizations 
FCMap(sv0weightmatlist[[1]][ROIdf_cortical_ordered$old_index,ROIdf_cortical_ordered$old_index],plottitle="first PC V02",negmax=-0.03,posmax=0.03,comms_df = Gordoncomms)
FCMap(sv2weightmatlist[[1]][ROIdf_cortical_ordered$old_index,ROIdf_cortical_ordered$old_index],plottitle="first PC V03",negmax=-0.03,posmax=0.03,comms_df = Gordoncomms)
#FCMap(sv4weightmatlist[[1]],plottitle="first PC year 4",negmax=-0.03,posmax=0.03,comms_df = Gordoncomms)

```

### 8) Output weights as tsvs brain-based visualization walkthrough

R is excellent at exporting tsvs, which can then be converted to pconns using `workbench`. The code repository contains a script that will automatically generate pconns and pscalars from output TSVs. Users can change the tsv output by editing step 7.10, reprinted below. Change the `fileroot` to modify the ouptut filenames. Change the `filepath` to modify where the outputs will be located.

```{r}
WritePCOutputs(sv0weightmatlist,fileroot="V02_PC_weights_for_strsup_scaled_score",filepath="~/HDCC_Sandbox_tutorials/examples/XCP_D_multivariate_prediction/Results/V02_weights")
WritePCOutputs(sv2weightmatlist,fileroot="V03_PC_weights_for_strsup_scaled_score",filepath="~/HDCC_Sandbox_tutorials/examples/XCP_D_multivariate_prediction/Results/V03_weights")
```